A Catalogue of Twists of Supersymmetric Gauge Theories

### 2020-01-22 paper.tex
N=2

\vspace{-10pt}
\paragraph{Fields:} The BRST fields are given by:
\begin{itemize}
\item Gauge fields $A_{1, 0} \in \Omega^{1, 0}(M; \fg)$, $A_{0, 1}\in\Omega^{0, 1}(M; \fg)$.
\item Gauge fermions $\chi\in\Omega^0(M; \Pi\fg)$, $\xi\in\Omega^{3, 0}(M; \Pi\fg)$, $B\in\Omega^{0, 2}(M; \Pi\fg)$, $\rho\in\Omega^{1, 0}(M; \Pi\fg)$.
\item Matter bosons $\nu\in\Omega^0(M; U\otimes K^{-1/2})$, $\phi\in\Omega^0(M; U\otimes K^{1/2})$.
\item Matter bosons $\nu\in\Omega^{3,0}(M; U)$, $\phi\in\Omega^0(M; U)$.
\item Matter fermions $\psi\in \Omega^{0, 1}(M; \Pi U\otimes K^{1/2})$, $\wt\nu\in\Omega^0(M; \Pi U\otimes K^{-1/2})$.
\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
\end{itemize}

@@

This theory admits a unique twist, which is necessarily of rank $1$:
\begin{itemize}
\item A square-zero supercharge $Q\neq 0\in\Sigma$ has 2 invariant directions, so it gives rise to a holomorphic theory. 
The identity homomorphism $\alpha = {\rm id} \colon \U(1)\rightarrow \U(1)$ given by the identity, makes $Q$ weight $+1$, so in this case we get a $\ZZ$-grading. 
Such a supercharge is stabilized by $G=\SU(2)$. 
Also, we have a compatible twisting homomorphism 
\[
\phi : \MU(2) \to {\rm Spin}(4) \times U(1) 
\]
where on the first component is the map $\MU(2) \to {\rm Spin}(4)$ lifting $\U(2) \to \SO(4)$ and on the second component $\MU(2) \to U(1)$ is the square root of determinant. 
\end{itemize}

@@

Under the embedding $\MU(L) = \MU(2) \subset \Spin(\VV_\RR)$, the spin representations decompose as
\[
S_+ = \det(L)^{-1/2} \oplus \det(L)^{1/2} \;\; , \;\; S_- = L \otimes \det(L)^{-1/2} .
\]
Moreover, under the twisting homomorphism
\[
\phi = \det \, ^{1/2} : \MU(2) \to \U(1)
\]
we have an identification $W = \det(L)^{1/2}$. 
By construction, $Q_+$ lies in the first factor of $S_+ \otimes W = \CC \oplus \det(L)$.

@@

We consider the twisting homomorphism 
\[
\phi \colon \MU(2) \xto{\det^{1/2}} U(1) \hookrightarrow \U(2)
\]
under which $Q$ becomes scalar.

@@

\vspace{-10pt}
\paragraph{Fields:} The BRST fields are given by:
\begin{itemize}
\item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(M; \gg)$ and $A_{0, 1}\in\Omega^{0, 1}(M; \gg)$.
\item Gauge scalar fields $\Tilde{a} \in \Omega^{0}(M; \gg)$ and $a \in\Omega^{0}(M; \gg)$;
\item Gauge fermions $\chi \in \Omega^0(M ; \Pi \gg)$, $\xi \in \Omega^{2,0}(M ; \Pi \gg)$, $B \in \Omega^{0,2}(M ; \gg)$, $b \in \Omega^{0,1}(M ; \gg)$, $\Tilde{\chi} \in \Omega^0(M ; \gg)$.
%\item Matter bosons $\nu \in \Omega^0(M ; U \otimes K^{-1/2})$, $\phi \in \Omega^0(M ; U \otimes K^{1/2})$.
\item Matter bosons $\nu\in\Omega^{2,0}(M; U)$, $\phi\in\Omega^0(M; U)$.
%\item Matter fermions $\psi \in \Omega^{0,1} (M ; \Pi U \otimes K^{1/2})$, $\varphi \in \Omega^{0} (M ; U \otimes K^{1/2})$, $\Tilde{\nu} \in \Omega^0(M ; U \otimes K^{-1/2})$.
\item Matter fermions $\psi \in \Omega^{0,1} (M ; \Pi U)$, $\varphi \in \Omega^{2,0} (M ; U)$, $\Tilde{\nu} \in \Omega^{0}(M ; U \otimes K^{-1})$.
\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
\end{itemize}

@@

We are left to check that the equivalence respects  the gradings and the $\MU(2)$-action. Indeed, the equivalence given by Theorem \ref{thm:5dminimaltwist} eliminates fields $A_{1, 0}, \Tilde{a}, \rho, \chi, \Tilde{\chi}$ and hence the underlying local $L_\infty$ algebra after the twist becomes
\[
\xymatrix@R=0.5cm@C=0.5cm{
\ul{0} & \ul{1} & \ul{2} & \ul{3} & \\ 
\Omega^0(\CC^2; \gg)_c \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{B} \\
 & \Omega^0(\CC^2; \gg)_a \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{b} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{\xi^*} \\
& \Omega^0(\CC^2 ; U)_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U)_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U)_{\varphi^*} \\
\Omega^{2,0}(\CC^2 ; U)_{\varphi} \ar[r] & \Omega^{2,1}(\CC^2 ; U)_{\psi^*} \ar[r] & \Omega^{2,2}(\CC^2 ; U)_{\phi^*} \\
 & \Omega^{2,0}(\CC^2 ; \gg)_{B^*} \ar[r] & \Omega^{2,1}(\CC^2 ; \gg)_{A_{0,1}^*} \ar[r] & \Omega^{2,2}(\CC^2 ; \gg)_{c^*} \\
 \Omega^{2,0}(\CC^2; \gg)_\xi \ar[r] &\Omega^{2,1}(\CC^2; \gg)_{b^*} \ar[r] &\Omega^{2,2}(\CC^2; \gg)_{a^*} 
}
\]
concentrated in cohomological degrees $0, \dots, 3$. These fields have the same degrees as in the holomorphic BF theory and the $L_\infty$ structure is obtained by the natural square zero extension of the dg Lie algebra in the first line by the remaining part of the diagram.
\end{proof}

@@

\brian{I've copied over Chris' work to another file and am working on it there.}

>>>>

\vspace{-10pt}
\paragraph{Fields:} The BRST fields are given by:
\begin{itemize}
\item Gauge fields $A_{1, 0} \in \Omega^{1, 0}(M; \fg)$, $A_{0, 1}\in\Omega^{0, 1}(M; \fg)$.
\item Gauge fermions $\chi\in\Omega^0(M; \Pi\fg)$, $\xi\in\Omega^{3, 0}(M; \Pi\fg)$, $B\in\Omega^{0, 2}(M; \Pi\fg)$, $\rho\in\Omega^{1, 0}(M; \Pi\fg)$.
\item Matter bosons $\nu\in\Omega^0(M; U\otimes K^{-1/2})$, $\phi\in\Omega^0(M; U\otimes K^{1/2})$.
\item Matter fermions $\psi\in \Omega^{0, 1}(M; \Pi U\otimes K^{1/2})$, $\wt\nu\in\Omega^0(M; \Pi U\otimes K^{-1/2})$.
\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
\end{itemize}

@@

This theory admits a unique twist, which is necessarily of rank $1$:
\begin{itemize}
\item A square-zero supercharge $Q\neq 0\in\Sigma$ has 2 invariant directions, so it gives rise to a holomorphic theory. 
The identity homomorphism $\alpha = {\rm id} \colon \U(1) \cong G_R$ makes $Q$ weight $+1$, so in this case we get a $\ZZ$-grading on the twisted theory. 
Such a supercharge is stabilized by $\SU(2)$. 
Also, we have a compatible twisting homomorphism 
\[
\phi : \MU(2) \to {\rm Spin}(4) \times U(1) 
\]
where on the first component is the map $\MU(2) \to {\rm Spin}(4)$ lifting $\U(2) \to \SO(4)$ and on the second component $\det^{1/2} : \MU(2) \to U(1)$ is the square root of determinant. 
\end{itemize}

@@

Under the embedding $\MU(L) = \MU(2) \subset \Spin(\VV_\RR)$, the spin representations decompose as
\[
S_+ = \det(L)^{-1/2} \oplus \det(L)^{1/2} \;\; , \;\; S_- = L \otimes \det(L)^{-1/2} .
\]

We consider the twisting homomorphism
\[
\phi = \det \, ^{1/2} : \MU(2) \to \U(1)
\]
for which $Q_+$ becomes a scalar.
Under this twisting homomorphism, we have an $\MU(2)$-identification $W = \det(L)^{1/2}$. 
By construction, $Q_+$ lies in the first factor of $S_+ \otimes W = \CC \oplus \det(L)$.

Since we have an isomorphism $\alpha : U(1) \cong G_R$ the twisted theory is $\ZZ$-graded.

@@

We consider the twisting homomorphism 
\[
\phi \colon \MU(2) \xto{\det^{1/2}} U(1) \hookrightarrow \U(2)
\]
for which $Q$ becomes scalar. 
\brian{I think we want that second map to be $1 \mapsto (1, -1)$, actually.}
Under this twisting homomorphism we have an $\MU(2)$-identification $W = \det(L)^{1/2} \oplus \det(L)^{1/2}$ and hence $S_+ \otimes W = (\CC \oplus \det(L))^{\oplus 2}$.
By construction, $Q_+$ lies in the first scalar factor.

The last piece of the twisting data is the homomorphism $\alpha : \U(1) \hookrightarrow \U(2)$ which embeds diagonally into the Cartan of $\U(2)$. 
This homomorphism is compatible with the twisting homomorphism $\phi$, so the twisted theory is $\ZZ$-graded.
\brian{check that $\phi$ and $\alpha$ commute.}

@@

\vspace{-10pt}
\paragraph{Fields:} The BRST fields are given by:
\begin{itemize}
\item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(M; \gg)$ and $A_{0, 1}\in\Omega^{0, 1}(M; \gg)$.
\item Gauge scalar fields $\Tilde{a} \in \Omega^{0}(M; \gg)$ and $a \in\Omega^{0}(M; \gg)$;
\item Gauge fermions $\chi \in \Omega^0(M ; \Pi \gg)$, $\xi \in \Omega^{2,0}(M ; \Pi \gg)$, $B \in \Omega^{0,2}(M ; \gg)$, $b \in \Omega^{0,1}(M ; \gg)$, $\rho \in \Omega^{1,0}(M ; \gg)$,  $\Tilde{\chi} \in \Omega^0(M ; \gg)$.
%\item Matter bosons $\nu \in \Omega^0(M ; U \otimes K^{-1/2})$, $\phi \in \Omega^0(M ; U \otimes K^{1/2})$.
\item Matter bosons $\nu\in\Omega^{0,0}(M; U)$, $\phi\in\Omega^0(M; U)$.
%\item Matter fermions $\psi \in \Omega^{0,1} (M ; \Pi U \otimes K^{1/2})$, $\varphi \in \Omega^{0} (M ; U \otimes K^{1/2})$, $\Tilde{\nu} \in \Omega^0(M ; U \otimes K^{-1/2})$.
\item Matter fermions $\psi \in \Omega^{0,1} (M ; \Pi U)$, $\varphi \in \Omega^{2,0} (M ; U)$, $\Tilde{\nu} \in \Omega^{0}(M ; U \otimes K^{-1})$.
\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
\end{itemize}

@@

Next, we check that the equivalence respects  the gradings and the $\MU(2)$-action. 
Indeed, the equivalence given by Theorem \ref{thm:5dminimaltwist} eliminates fields $A_{1, 0}, \Tilde{a}, \rho, \chi, \Tilde{\chi}$ and hence the underlying local $L_\infty$ algebra after the twist becomes
\[
\xymatrix@R=0.5cm@C=0.5cm{
\ul{0} & \ul{1} & \ul{2} & \ul{3} & \\ 
\Omega^0(\CC^2; \gg)_c \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{B} \\
 & \Omega^0(\CC^2; \gg)_a \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{b} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{\xi^*} \\
& \Omega^0(\CC^2 ; U)_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U)_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U)_{\varphi^*} \\
\Omega^{2,0}(\CC^2 ; U)_{\varphi} \ar[r] & \Omega^{2,1}(\CC^2 ; U)_{\psi^*} \ar[r] & \Omega^{2,2}(\CC^2 ; U)_{\phi^*} \\
 & \Omega^{2,0}(\CC^2 ; \gg)_{B^*} \ar[r] & \Omega^{2,1}(\CC^2 ; \gg)_{A_{0,1}^*} \ar[r] & \Omega^{2,2}(\CC^2 ; \gg)_{c^*} \\
 \Omega^{2,0}(\CC^2; \gg)_\xi \ar[r] &\Omega^{2,1}(\CC^2; \gg)_{b^*} \ar[r] &\Omega^{2,2}(\CC^2; \gg)_{a^*} 
}
\]
concentrated in cohomological degrees $0, \dots, 3$. These fields have the same degrees as in the holomorphic BF theory and the $L_\infty$ structure is obtained by the natural square zero extension of the dg Lie algebra in the first line by the remaining part of the diagram.
Finally, we observe that the twisted theory manifestly descends to a $\U(2)$-equivariant theory along the natural homomorphism $\MU(2) \to \U(2)$, and all identifications are $\U(2)$-equivariant. 
\end{proof}

@@

Next we discuss the case of the topological twist. 
We are going to prove that it is perturbatively trivial. 
In fact, it will be useful to study a degeneration of the topological twist to a holomorphic twist and describe the corresponding family of twisted theories.

Let $V_\RR = \RR^4$ and $V=V_\RR\otimes_\RR\CC$. 
Fix a K\"ahler structure on $\RR^4$ and denote by $L\subset V$ the $i$-eigenspace of the complex structure. %Moreover, fix a complex volume form on $L$.

We will use the notation for fields of 4d $\cN=1$ super Yang--Mills from Section \ref{sect:8dholomorphictwist}. 
First, we are going to write the functionals \eqref{eq:gaugeI1}, \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2} in terms of these fields.

\begin{prop}
Suppose $Q_t$ is the rank $(2,0)$ supercharge as above.
The $\MU(2)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 4d $\cN=2$ super Yang--Mills theory are
\begin{align*}
I_{\rm gauge}^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(b, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}a, b^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2} \xi^*\wedge B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t a c^*\right).
\end{align*}
\end{prop}
\begin{proof}
We first write down the functionals in $\Spin(4)$-notation.
The fields of $4d \cN=2$ decompose as:
\begin{itemize}
 \item $\gg$-valued Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and a pair of scalar fields $(a ,\Tilde{a}) \in \Omega^0(\RR^4; \gg \oplus \gg)$.
 \item $U$-valued bosons: a $W$-valued scalar field $\phi \otimes v \in \Omega^0(\RR^4; W \otimes U)$.
 \item $\gg$-valued fermions: a $W$-valued Dirac spinor $\lambda = (\lambda_+ \otimes u_+, \lambda_-\otimes u_-) \in \Omega^0(\RR^4; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
 \item $U$-valued fermions: a Dirac spinor $\psi = (\psi_+,\psi_-) \in \Omega^0(\RR^4; (S_+\oplus S_-) \otimes U)$.
 \item a ghost $c \in \Omega^0(\RR^4 ; \gg)$.
\end{itemize}

\brian{If we split $V^{6d}$ as $V^{4d} \oplus N \oplus N^*$ where $N, N^*$ are trivial one-dimensional $\Spin(4)$-representations, then $W^{4d} = W_+^{6d} \otimes N$ and $W^{4d*} = W_+^{6d} \otimes N^*$. 
Moreover, the isomorphism $\wedge^2 S_+^{6d} \cong V^{6d}$ gives rise to three maps
\begin{itemize}
\item $S^{4d}_+ \otimes S^{4d}_- \otimes N \otimes N^* \to V^{4d}$. This is $\Gamma^{4d} \otimes {\rm ev}_N$. 
\item $\wedge^2(S_+^{4d} \otimes N) \to N^*$. 
\item $\wedge^2(S_-^{4d} \otimes N^*) \to N$. 
\end{itemize}
The bosons in the gauge part live in $a \in N^*$ and $\Tilde{a} \in N$. 
For $Q_+ \in S^{4d}_+ \otimes W^{4d} = S^{4d}_+ \otimes W^{6d}_+ \otimes N$ and $\lambda_+ \in S^{4d}_+ \otimes W^{4d} = S^{4d}_+ \otimes W^{6d}_+ \otimes N$. 
I want to make sense of $(\<Q_+, \lambda_+\> , \Tilde{a}^*)$ as a scalar via the composition
\[
\wedge^2 (S_+^{4d} \otimes W^{6d}_+ \otimes N) \otimes N  \xto{\omega_{W_+}} \wedge^2(S^{4d}_+ \otimes N) \otimes N \to N^* \otimes N \to \CC .
\]
The first map is the symplectic pairing on $W_+$. 
The second map is the second bullet above. 
The last map is evaluation.
Do you see an easier way to canonically write this using only 4d objects?
}

For a general supercharge $Q_+ \in S_+ \otimes W$, the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ decompose as:
\begin{align*}
I^{(1)}_{\mr{gauge}}(Q_+) &= \int \dvol \bigg(-( (\Gamma(Q_+,\lambda_-), A^*) + \langle Q_+,\lambda_+\rangle w_+ \wedge u_+, \phi_2^* ) + \\
&\qquad  + \frac 12 ((\rho(F_A)Q_+, \lambda_+^*)(u_+^*,  w_+) + (\rho(\d_A \phi_2(w_+ \wedge u_-^*))Q_+, \lambda_-^*) \bigg)\\
I^{(1)}_{\mr{matter}}(Q) &= \int \dvol (((Q_+,\psi_+), \phi^*)(v^*,w_+) + \frac 12 (\rho(\d_A \phi)Q_+, \psi_+^*)(v,w_+)) \\
I^{(2)}_{\mr{gauge}}(Q,Q) &= \int \dvol \big(\frac 14 (Q_+,Q_+)(\lambda_-,\lambda_-)(u_-,w_+)^2 - \frac 12  (Q_+, \lambda_-^*)^2(w_+ \wedge u_-^*)^2 - (Q_+,Q_+)\phi_1(w_+ \wedge w_+)c^* \big) \\
I^{(2)}_{\mr{matter}}(Q,Q) &= \int \frac 14 \dvol (Q_+,Q_+)(\psi_-^*,\psi_-^*)(w_-^* \wedge w_-^*)
\end{align*}
if $Q=Q_+ \otimes w_+$ is a non-zero element of $S_+ \otimes W$. \chris{missing thing here: trivialising those wedge pairs, or equivalently restricting $\Gamma(-,-)$ from 6d to 4d.}
